\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-10 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\section{Mechanism Design} \label{sec:mechanism_design}

@@

In summary, the entry of Lianjia into a segmented market initially results in a significant increase in revenue and facilitates a higher number of house tours, which, in turn, leads to greater price concessions. However, this positive impact is transient, diminishing over time due to increased market competition and external factors such as the COVID-19 pandemic. This suggests that while Lianjia's entry provides a short-term boost to its market performance, the sustainability of this effect is challenged by both competitive dynamics and unforeseen external shocks.

@@

Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%. Conversely, this effect is not significant in the lower HHI group and higher concentration group. This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially. However, the entry of offline stores have no influence on other groups. Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit. Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage. In the Appendix we also conducted the robustness check by classifying the market with low and high nighttime light areas and the results are reported in Appendix Table \ref{tab:robustness_nighttime_light_entry}.

We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}. For this test, we employed a neighborhood sample with randomly generated treatment effects. Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects. The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness_1}
      \input{../result_tables/entry_effect_hetero_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect (Continued)}
      \label{tab:entry_effect_robustness_2}
      \input{../result_tables/entry_effect_hetero_2.tex}

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis. In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also classified the samples to low and high nighttime light areas, and the results show that our results are robust.

@@

Section{Additional Robustness Check of Main Results} \label{sec:additional_robustness}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect}
      \label{tab:robustness_check_additional_1}
      \input{../result_tables/entry_robust_adding_variables_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect (Continued)}
      \label{tab:robustness_check_additional_2}
      \input{../result_tables/entry_robust_adding_variables_2.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect}
      \label{tab:robustness_check_platform_1}
      \input{../result_tables/plat_robust_adding_variables_1.tex}

@@

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Offline Expansion Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_entry}
      \input{../result_tables/entry_light_robustness.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Platform Consolidation Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_consolidation}
      \input{../result_tables/plat_light_robustness.tex}

@@

>>>>

\section{Estimation of Offline Expansion Effect and Online-Mediated Consolidation Effect} \label{sec:mechanism_design}

@@

@@

Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%. Conversely, this effect is not significant in the lower HHI group and higher concentration group. This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially. However, the entry of offline stores have no influence on other groups. Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit. Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage.

To further check the robustness of our results, we conducted another three tests. In the Appendix, we conducted the same estimation but without additional control variables and the results are reported in Appendix Table \ref{tab:entry_effect_robustness_1} and Appendix Table \ref{tab:entry_effect_robustness_2}. The estiamted results are shown consistent without additional control variabels. In the Appendix we also conducted the robustness check by classifying the market with low and high nighttime light areas and the results are reported in Appendix Table \ref{tab:robustness_nighttime_light_entry}.

We also conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}. For this test, we employed a neighborhood sample with randomly generated treatment effects. Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects. The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness_1}
      \input{../result_tables/entry_effect_hetero_1.tex}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect (Continued)}
      \label{tab:entry_effect_robustness_2}
      \input{../result_tables/entry_effect_hetero_2.tex}

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings.

Same as the Section \ref{subsec:entry_effect}, we performed the estimation without incorporating additional control variables, as documented in Appendix Table \ref{tab:robustness_check_platform_1} and Appendix Table \ref{tab:robustness_check_platform_2}. The findings remain consistent with our initial estimates. In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also categorize the sample into areas with low and high nighttime light. The results from this stratification further corroborate the robustness of our original conclusions.

We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis.

@@

\section{Additional Robustness Check of Main Results} \label{sec:additional_robustness}

@@

In this section, we report the robustness check of DID model. Table \ref{tab:robustness_check_additional_1}, Table \ref{tab:robustness_check_additional_2} display the estimation outcomes without the inclusion of additional control variables. By comparing these results with those obtained when controls are included, we observe that the estimates remain consistent across different model specifications. This consistency indicates the robustness of our findings, reinforcing the validity of our conclusions.

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect}
      \label{tab:robustness_check_additional_1}
      \input{../result_tables/entry_robust_adding_variables_1.tex}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect (Continued)}
      \label{tab:robustness_check_additional_2}
      \input{../result_tables/entry_robust_adding_variables_2.tex}

@@

Table \ref{tab:robustness_check_platform_1} and \ref{tab:robustness_check_platform_2} shows the results or our estimation with or without additional control variables, and the results are consistent.

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect}
      \label{tab:robustness_check_platform_1}
      \input{../result_tables/plat_robust_adding_variables_1.tex}

@@

Figure \ref{fig:treatment_consolidation} shows the statistical summary of the Lianjia's summary with the treatment group and the control grouls. We can see that the general trend is similar to the estimation results.

@@

Table \ref{tab:robustness_nighttime_light_entry} and Table \ref{tab:robustness_nighttime_light_consolidation} show the additional results of the DID model by classifying the samples to low and high nighttime light areas. The results show that there is heterogeneity effect across different areas, but the general estimation results are in line with our main model.

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Offline Expansion Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_entry}
      \input{../result_tables/entry_light_robustness.tex}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Platform Consolidation Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_consolidation}
      \input{../result_tables/plat_light_robustness.tex}

@@

Figure \ref{fig:placebo_test_entry} and Figure \ref{fig:placebo_test_plat} show the results of the placebo test for the entry effect and the platform consolidation effect. The results show that the random treatment effect is non-significant at the 10\% level, indicating that the treatment effect is not due to other factors.
